Evaluation of performances

### 2021-04-09 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE,     verbose = TRUE)

```{r eval-performance-1, warning=FALSE}
table1 <- df_perf %>%
  group_by(learner.id, task.id, filter) %>%
  slice(which.min(rmse_aggr)) %>%
  dplyr::rename(
    "Model" = learner_group,
    "Learner ID" = learner.id,
    "Task" = task.id,
    "Filter" = filter,
    "RMSE" = rmse_aggr,
    "SE" = se,
  ) %>%
  ungroup() %>%
  mutate(Filter = replace(Filter, is.na(Filter), "No Filter")) %>%
  select(-iter, -`Learner ID`) %>%
  mutate(RMSE = round(RMSE, 3)) %>%
  arrange(RMSE)

# save as latex table
table1 %>%
  ungroup() %>%
  arrange(RMSE) %>%
  slice(1:10) %>%
  xtable(
    type = "latex",
    caption = "Best ten results among all combinations, sorted in ascending order of RMSE",
    label = "tab:perf-top-10"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-top-10.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

```{r eval-performance-2, warning=FALSE}
table2 <- df_perf %>%
  group_by(learner_group) %>%
  slice(which.min(rmse_aggr)) %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  arrange(rmse_aggr) %>%
  dplyr::rename(
    "Model" = learner_group,
    "Learner ID" = learner.id,
    "Task" = task.id,
    "Filter" = filter,
    "RMSE" = rmse_aggr,
    "SE" = se,
  ) %>%
  select(-iter) %>%
  select(-`Learner ID`)

# save as latex table
table2 %>%
  xtable(
    type = "latex",
    caption = "Best performance of each learner across any task and filter method, sorted ascending by RMSE",
    label = "tab:best-learner-perf"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-best-per-learner.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    scalebox = 0.90,
    caption.placement = "top",
    timestamp = NULL
  )

@@

```{r eval-performance-3, warning=FALSE}
table3 <- df_perf %>%
  group_by(learner.id, task.id, filter) %>%
  slice(which.min(rmse_aggr)) %>%
  dplyr::rename(
    "Model" = learner_group,
    "Learner ID" = learner.id,
    "Task" = task.id,
    "Filter" = filter,
    "RMSE" = rmse_aggr,
    "SE" = se,
  ) %>%
  ungroup() %>%
  mutate(Filter = replace(Filter, is.na(Filter), "No Filter")) %>%
  select(-iter, -`Learner ID`, -SE) %>%
  mutate(RMSE = round(RMSE, 3)) %>%
  arrange(RMSE)

# save as latex table
table3 %>%
  ungroup() %>%
  arrange(desc(RMSE)) %>%
  slice(1:10) %>%
  xtable(
    type = "latex",
    caption = "Worst ten results among all combinations, sorted in decreasing order of RMSE",
    label = "tab:perf-worst-10"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-worst-10.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

# define appearance of \multirow
df_tbl[[1]][first] <-
  paste0("\\midrule\\multirow{", rle.lengths, "}{*}{\\specialcell{", df_tbl[[1]][first], "}}")
# remove redundant midrule from first entry
df_tbl[[1]][first][1] = gsub("\\\\midrule", "", df_tbl[[1]][first][1])

>>>>

```{r eval-performance-1, warning=FALSE}
table1 <- df_perf %>%
  group_by(learner.id, task.id, filter) %>%
  slice(which.min(rmse_aggr)) %>%
  mutate(rsq = round(rsq, 3)) %>%
  dplyr::rename(
    "Model" = learner_group,
    "Learner ID" = learner.id,
    "Task" = task.id,
    "Filter" = filter,
    "RMSE" = rmse_aggr,
    "SE (RMSE)" = se,
    "R^2" = rsq,
  ) %>%
  ungroup() %>%
  mutate(Filter = replace(Filter, is.na(Filter), "No Filter")) %>%
  select(-iter, -`Learner ID`, -expvar) %>%
  relocate(RMSE, .after = Filter) %>%
  relocate(`SE (RMSE)`, .after = RMSE) %>%
  mutate(RMSE = round(RMSE, 3)) %>%
  arrange(RMSE)

# save as latex table
table1 %>%
  ungroup() %>%
  arrange(RMSE) %>%
  slice(1:10) %>%
  xtable(
    type = "latex",
    caption = "Best ten results among all combinations, sorted in ascending order of RMSE",
    label = "tab:perf-top-10"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-top-10.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL,
    sanitize.text.function = function(x) {
      x
    }
  )

@@

```{r eval-performance-2, warning=FALSE}
table2 <- df_perf %>%
  group_by(learner_group) %>%
  slice(which.min(rmse_aggr)) %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  arrange(rmse_aggr) %>%
  mutate(rsq = round(rsq, 3)) %>%
  dplyr::rename(
    "Model" = learner_group,
    "Learner ID" = learner.id,
    "Task" = task.id,
    "Filter" = filter,
    "RMSE" = rmse_aggr,
    "SE (RMSE)" = se,
    "R^2" = rsq,
  ) %>%
  select(-`Learner ID`) %>%
  relocate(RMSE, .after = Filter) %>%
  relocate(`SE (RMSE)`, .after = RMSE) %>%
  select(-iter, -expvar)

# save as latex table
table2 %>%
  xtable(
    type = "latex",
    caption = "Best performance of each learner across any task and filter method, sorted ascending by RMSE",
    label = "tab:best-learner-perf"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-best-per-learner.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    scalebox = 0.90,
    caption.placement = "top",
    timestamp = NULL,
    sanitize.text.function = function(x) {
      x
    }
  )

@@

```{r eval-performance-3, warning=FALSE}
table3 <- df_perf %>%
  group_by(learner.id, task.id, filter) %>%
  slice(which.min(rmse_aggr)) %>%
  mutate(rsq = round(rsq, 3)) %>%
  dplyr::rename(
    "Model" = learner_group,
    "Learner ID" = learner.id,
    "Task" = task.id,
    "Filter" = filter,
    "RMSE" = rmse_aggr,
    "R^2" = rsq,
    "SE" = se,
    "SE (RMSE)" = se
  ) %>%
  ungroup() %>%
  mutate(Filter = replace(Filter, is.na(Filter), "No Filter")) %>%
  select(-iter, -`Learner ID`, -expvar) %>%
  relocate(RMSE, .after = Filter) %>%
  relocate(`SE (RMSE)`, .after = RMSE) %>%
  mutate(RMSE = round(RMSE, 3)) %>%
  arrange(RMSE)

# save as latex table
table3 %>%
  ungroup() %>%
  arrange(desc(RMSE)) %>%
  slice(1:10) %>%
  xtable(
    type = "latex",
    caption = "Worst ten results among all combinations, sorted in decreasing order of RMSE",
    label = "tab:perf-worst-10"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-worst-10.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL,
    sanitize.text.function = function(x) {
      x
    }
  )

@@

# define appearance of \multirow
df_tbl[[1]][first] <-
  paste0("\\midrule\\multirow{", rle.lengths, "}{*}{\\specialcell{", df_tbl[[1]][first], "}}")
# remove redundant midrule from first entry
df_tbl[[1]][first][1] <- gsub("\\\\midrule", "", df_tbl[[1]][first][1])
